\section{Supplementary material}\label{sec:supp_material}
\gard{Let's move at least the simplex count table here. NeurIPS says: \emph{This length does not include references or any supplementary materials. Reviewers are not obliged to read supplementary materials when reviewing the paper.}}

\textbf{Co-authorship complexes.} A co-authorships complex is built by adding a $(k-1)$-simplex for each paper with $k$ authors. The added subsimplices of the $k-1$-simplex are interpreted as collaboration in writing the

We report in the following table the number of simplices in dimension $k=0,1,2$ of the co-authorship complexes CC1 and CC2.
\begin{table}[htbp]
  \centering
  \scriptsize{
  \begin{tabular}{llllllllllll}
    \cmidrule(r){1-12}
    Dimension:   & 0     & 1  & 2     & 3 & 4     & 5 & 6    & 7 & 8   & 9 & 10\\
    \midrule
    CC1 & 352  & 1474  & 3285  & 5019  & 5559  & 4547  & 2732  & 1175  & 343 & 61 & 5\\
    CC2 & 1126 & 5059 & 11840 & 18822 & 21472 & 17896  & 10847 & 4673 & 1357 & 238 & 19\\ 
    \bottomrule
  \end{tabular}}
  \vspace{2pt}
  \caption{%
  Number of simplices in co-authorship complexes from the Semantic Scholar dataset.
  } \label{table:Simplices-coauthor}
\end{table}
\stefania{Kathryn-Gard: what do you think about adding here the distribution of the values of the citations?}
\gard{A nice addition if you have the time (but I wouldn't prioritize it).}

\textbf{Glossary Missing Data Imputation.} We state here some definitions and criteria that are used in the results section. 
A missing value is predicted correctly if the imputed value differs of at most $1$ from the actual values. 
The \emph{accuracy} is defined as the percentage of missing values that has been correctly imputed and the \emph{absolute error} (AE) as the magnitude of the difference between the predicted and actual citation.
For the same percentage of missing values we consider different random samples of the damaged portions. Then a statistical evaluation of the performance of the network is given by the \emph{mean accuracy} (MA), the mean of the accuracy over different samples and the \emph{mean absolute error distribution}(MAED), the average distribution of the error over different samples.
